Automated topic naming to support analysis of software maintenance activities

### 2011-01-10 msr/msr2011.tex
More intro fiddling
migod's abstract

\author{
\alignauthor 
Abram Hindle\\
   \affaddr{Department of Computer Science}\\
   \affaddr{University of California, Davis} \\
   \affaddr{Davis, CA, USA}\\
   \email{abram.hindle@softwareprocess.es}
\alignauthor  Neil A. Ernst\\
   \affaddr{Department of Computer Science}\\
   \affaddr{University of Toronto}\\
   \affaddr{Toronto, Ontario, CANADA}\\
   \email{nernst@cs.toronto.edu}
\and
\alignauthor Michael W. Godfrey\\
   \affaddr{David Cheriton School of Computer Science}\\
   \affaddr{University of Waterloo}\\
   \affaddr{Waterloo, Ontario, CANADA}\\
   \email{migod@uwaterloo.ca}
\alignauthor John Mylopoulos \\
   \affaddr{Department of Computer Science}\\
   \affaddr{University of Toronto}\\
   \affaddr{Toronto, Ontario, CANADA}\\
   \email{jm@cs.toronto.edu}
}

@@

Researchers have used topic modeling and concept location to understand the latent topics of software development artifacts.
These techniques use unsupervised machine-learning algorithms to recover topics.
These topics are word-lists and are difficult to distinguish and interpret. 
Topics are not meaningful until they have been named or interpreted.
Current topic labelling approaches are manual, and do not use domain-specific knowledge to improve, contextualize, or describe results for the developers.
We propose a solution: \emph{labelled topic extraction}.
Topics are extracted using Latent Dirichlet Allocation (LDA) from commit-log comments recovered from source control systems such as CVS and BitKeeper. 
These topics are given labels relating to a generalizable cross-project taxonomy consisting of non-functional requirements.
Our approach was evaluated  with experiments and case studies on two large-scale RDBMS projects: MySQl and MaxDB.
Labelled topic extraction produces appropriate, context-sensitive labels relevant to these projects, which provides fresh insight into their evolving software development activities.

@@

There are many practical applications of \emph{labelled topic
  extraction} 
ranging from summarization, project dashboards, and software process recovery.
These methods are useful for providing abstractions of development activities and artifacts.
Particularly in large projects, summarization of developer activities is essential to maintenance. 
Rather than looking for specific concepts in a project~\cite{marcus04wcre}, we are interested in understanding a software project relative to common properties of all software.
We can improve project dashboards, used by managers, by showing both the current topics of development as well those that relate to domain-independent taxonomies, such as NFRs.
Some quality assurance questions can be addressed by seeking evidence within repositories that NFR-related topics are being addressed.
Topic modelling can be used to check if development is on track and focused.
For outside users of the software, our technique can provide insight into that company's development practices in order to answer questions such as, ``Are they focused on usability?''
Within the organization \emph{labelled topic extraction} can act as a historical sanity check, used to avoid \emph{confirmation bias}, which is the difference between what people think happened and what actually happened. 
Some software releases, for instance, are poorly received since they are quite buggy. 
Our technique would help explain why this was the case, since it can identify NFRs which are dominating developer attention.
% This is a very long example it'd be nice if it was tighter
% Perhaps development has been sidetracked by cascading issues that appeared during implementation.
% For instance, a developer adding an optimization to a RDBMS might have to change multiple modules in order to provide that optimization code with enough information to operate. 
% This issue might trigger a series of cascading changes that might be difficult to discover when trying to explain why the project's release date has been missed. 
% Labelled Topic extraction could be used to detect this distinct focus of development.

>>>>

\author{
\alignauthor 
Abram Hindle\\
   \affaddr{Department of Computer Science}\\
   \affaddr{University of California, Davis} \\
   \affaddr{Davis, CA, USA}\\
   \email{abram@softwareprocess.es}
\alignauthor  Neil A. Ernst\\
   \affaddr{Department of Computer Science}\\
   \affaddr{University of Toronto}\\
   \affaddr{Toronto, Ontario, CANADA}\\
   \email{nernst@cs.toronto.edu}
\and
\alignauthor Michael W. Godfrey\\
   \affaddr{David Cheriton School of Computer Science}\\
   \affaddr{University of Waterloo}\\
   \affaddr{Waterloo, Ontario, CANADA}\\
   \email{migod@uwaterloo.ca}
\alignauthor John Mylopoulos \\
   \affaddr{Department of Computer Science}\\
   \affaddr{University of Toronto}\\
   \affaddr{Toronto, Ontario, CANADA}\\
   \email{jm@cs.toronto.edu}
}

@@

Researchers have employed a variety of techniques to extract underlying
topics that relate to software development artifacts.  Typically, these
techniques use unsupervised machine-learning algorithms to suggest
candidate word-lists that recur together often.  However, word-lists are
difficult to 
interpret in the absence of meaningful summary labels.  Current topic modeling 
techniques assume manual labelling and do not use domain-specific knowledge
to improve, contextualize, or describe results for the developers.  
We propose a solution: \emph{automated labelled topic extraction}.
  Topics are extracted 
using  Latent Dirichlet Allocation (LDA) from commit-log comments recovered
from source control systems such as CVS and BitKeeper.  
These topics are given labels relating to a generalizable
cross-project taxonomy, consisting of non-functional
requirements. Our approach was evaluated with experiments and case studies
on two large-scale RDBMS projects: MySQL and MaxDB.  The case studies
show that labelled topic extraction can produce appropriate,
context-sensitive labels relevant to these projects, which provides fresh
insight into their evolving software development activities.

% Researchers have used topic modeling and concept location to understand the latent topics of software development artifacts.
% These techniques use unsupervised machine-learning algorithms to recover topics.
% These topics are word-lists and are difficult to distinguish and interpret. 
% Topics are not meaningful until they have been named or interpreted.
% Current topic labelling approaches are manual, and do not use domain-specific knowledge to improve, contextualize, or describe results for the developers.
% We propose a solution: \emph{labelled topic extraction}.
% Topics are extracted using Latent Dirichlet Allocation (LDA) from commit-log comments recovered from source control systems such as CVS and BitKeeper. 
% These topics are given labels relating to a generalizable cross-project taxonomy consisting of non-functional requirements.
% Our approach was evaluated  with experiments and case studies on two large-scale RDBMS projects: MySQl and MaxDB.
% Labelled topic extraction produces appropriate, context-sensitive labels relevant to these projects, which provides fresh insight into their evolving software development activities.

@@

There are many practical applications of \emph{labelled topic
  extraction} 
ranging from summarization, project dashboards, and software process recovery.
These methods are useful for providing abstractions of development activities and artifacts.
Particularly in large projects, summarization of developer activities is essential to maintenance. 
Rather than looking for specific concepts in a project~\cite{marcus04wcre}, we are interested in understanding a software project relative to common properties of all software.
We can improve project dashboards, used by managers, by showing both the current topics of development as well those that relate to domain-independent taxonomies, such as NFRs.
Some quality assurance questions can be addressed by seeking evidence within repositories that NFR-related topics are being addressed.
Topic modelling can be used to check if development is on track and focused.
For outside users of the software, our technique can provide insight into that company's development practices in order to answer questions such as, ``Are they focused on usability?''
Within the organization \emph{labelled topic extraction} can act as a historical sanity check, used to avoid \emph{confirmation bias}, which is the difference between what people think happened and what actually happened. 
Some software releases, for instance, are poorly received since they are quite buggy. 
Our technique would help explain why this was the case, since it can identify NFRs which are dominating developer attention.
Thus developers can use these techniques to get an overview of the current and past development topics.
For awareness, managers can use these techniques to gain an overview of topics of development.

% This is a very long example it'd be nice if it was tighter
% Perhaps development has been sidetracked by cascading issues that appeared during implementation.
% For instance, a developer adding an optimization to a RDBMS might have to change multiple modules in order to provide that optimization code with enough information to operate. 
% This issue might trigger a series of cascading changes that might be difficult to discover when trying to explain why the project's release date has been missed. 
% Labelled Topic extraction could be used to detect this distinct focus of development.
